Data Preparation

### 2019-01-14 Data Preparation.Rmd
simplify code for extracting overviews

```{r extracting overview, cache = TRUE}
# Setup
n_catalogue <- length(corpus_catalogues)
calendar_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
d_description <- tibble(Code            = character(0),
                        `Calendar Year` = character(0),
                        Overview        = character(0))
course_code <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>%
  paste(collapse = "|")
content_to_exclude <- c("^Core Courses \\(COR\\)",
                        "^Humanities \\(HUM\\)",
                        "^Sciences \\(SCI\\)",
                        "^Social Sciences \\(SSC\\)",
                        "^Skills Trainings \\(SKI\\)",
                        "^Projects \\(PRO\\)",
                        "^Undergraduate Research \\(UGR\\)",
                        "Appendix") %>%
  paste(collapse = "|")
# Loop
for(n in 1 : n_catalogue){

@@

  pages_to_exclude     <- grep(pattern = content_to_exclude, x = cat)
  first_three_letters  <- substr(cat, start = 1, stop = 3)
  first_pages_overview <- grep(pattern = course_code, x = first_three_letters)

  page_start_loop <- grep(pattern = "^Core Courses \\(COR\\)", x = cat) + 1
  page_end_loop   <- length(cat)

  for(page in page_start_loop : page_end_loop){

    current_page           <- page
    following_page         <- page + 1
    current_page_content   <- cat[page          ]
    following_page_content <- cat[following_page]

    if(current_page %in% first_pages_overview){

      if(following_page %in% c(first_pages_overview, pages_to_exclude)) course_overview <- current_page_content
      else course_overview <- paste(current_page_content, following_page_content)
      # Save Overview
      Code <- substring(course_overview, first = 1, last = 7)      
      year <- calendar_years[n]
      d_description <- add_row(d_description,
                               Code            = Code,
                               `Calendar Year` = year,
                               Overview        = course_overview)
    } # close if-statement
  } # close for-loop (page)
} # close for-loop (n)
rm(corpus_catalogues,
   n_catalogue, calendar_years, course_code, content_to_exclude,
   n, cat, pages_to_exclude, first_three_letters, first_pages_overview, page_start_loop, page_end_loop,
   page, current_page, following_page, current_page_content, following_page_content,
   course_overview, Code, year)
print(d_description)
```

>>>>

```{r extracting overview, cache = TRUE}
# Setup
n_catalogue <- length(corpus_catalogues)
calendar_years <- c("2014-2015", "2015-2016", "2016-2017", "2017-2018", "2018-2019")
d_description <- tibble(Code            = character(0),
                        `Calendar Year` = character(0),
                        Overview        = character(0))

course_code <- c("COR", "HUM", "SCI", "SSC", "SKI", "PRO", "UGR", "CAP") %>%
  paste(collapse = "|")

content_to_exclude <- c(
  "^Core Courses \\(COR\\)",
  "^Humanities \\(HUM\\)",
  "^Sciences \\(SCI\\)",
  "^Social Sciences \\(SSC\\)",
  "^Skills Trainings \\(SKI\\)", "^Skills Training \\(SKI\\)",
  "^Project \\(PRO\\)", "^Projects \\(PRO\\)",
  "^Undergraduate Research \\(UGR\\)",
  " UCM Undergraduate\r\nResearch", "UCM Undergraduate\r\n  Research"
  ) %>%
  paste(collapse = "|")

# Loop 1
for(n in 1 : n_catalogue){

@@

  # Overview section in catalogue
  page_overview_start <- grep(pattern = "^Core Courses \\(COR\\)", x = cat) + 1
  page_overview_end   <- grep(pattern = "Appendix", x = cat) - 1
    if(length(page_overview_end) == 0) page_overview_end <- length(cat)
  cat_overview <- cat[page_overview_start : page_overview_end]

  # Course description only
  pages_to_exclude <- grep(pattern = content_to_exclude, x = cat_overview)
  cat_overview <- cat_overview[! 1 : length(cat_overview) %in% pages_to_exclude]

  # First pages of course overviews
  first_three_letters <- substr(cat_overview, start = 1, stop = 3)
  first_pages_overview <- grep(pattern = course_code, x = first_three_letters)

  # Loop 2
  for(page in first_pages_overview){

    # Extract description
    overview <- if(page + 1 %in% first_pages_overview) cat_overview[page]
                else paste(cat_overview[page : (page + 1)], collapese = " ")

    # Save overview
    Code <- substr(overview, start = 1, stop = 7)
    year <- calendar_years[n]
    d_description <- d_description %>%
      add_row(
        Code = Code,
        `Calendar Year` = year,
        Overview = overview
      )

  } # close for-loop (page)

} # close for-loop (n)

rm(corpus_catalogues,
   n_catalogue, calendar_years, course_code, content_to_exclude,
   n, cat,
   page_overview_start, page_overview_end,
   pages_to_exclude, cat_overview,
   first_three_letters, first_pages_overview,
   page, overview, Code, year)
print(d_description)
```
